### 2022-05-15 template/fantemplate_acceptedsubmit/manuscript_online_appendix.tex
Accepted Template preprint + journal submit tex/pdf

% reset page numbers
\pagenumbering{arabic}
\setcounter{page}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title Page for Appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% special footnote symbols
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\begingroup
  \doublespacing
  \centering
  \Large ONLINE APPENDIX \\[1.5em]
  \LARGE \PAPERTITLE \\[0.75em]
  \large
    Fan Wang,\footnote[1]{\AUTHORWANG}\\[1.0em]
\endgroup
\clearpage

@@

We include in the estimation children who were born between 1970 and 1975. We show summary statistics for these children in Sections \ref{sec:stat} and \ref{sec:gap}. As discussed earlier, we do not observe both initial heights and heights at month 24 for children born before or after these years.

We use the months 15 to 24 average protein intakes, heights at month 24, protein prices, incomes, gender, and initial height variables shown in Table \ref{summcovarmain} and described in Section \ref{sec:stat} as $N$, $H^{24}$, $p_{yv}^{N}$, $Y$, and components of $X$. We use protein intakes because \textcite{puentes_early_2016} shows that proteins rather than non-protein components of calories matter for height growth in these INCAP data. Ideally, our intake variable should be averaged from month 0 to month 24. However, we do not observe protein values from month 0 to month 12 for close to half of our sample because data collection for this age group started in 1973. Also, it is not easy to estimate the protein component of breastmilk for children who rely on breastfeeding in the first year of life.

@@

For $\rho$, the quadratic coefficient on non-nutritional consumptions, the estimated coefficient becomes more negative as $\sigma_{R_{y,v}}$ increases. This finding implies lower marginal gains from additional non-nutritional consumption at higher $\sigma_{R_{y,v}}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Appendix Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Bibliography
\begingroup
\setstretch{1.0}
\setlength\bibitemsep{0pt}
\printbibliography[title=References for Online Appendix]
\endgroup
\pagebreak

>>>>

@@

We include in the estimation children who were born between 1970 and 1975. We show summary statistics for these children in Sections \ref{sec:stat} and \ref{sec:gap}.\footnote{As discussed earlier, we do not observe both initial heights and heights at month 24 for children born before or after these years.}

We use the months 15 to 24 average protein intakes, heights at month 24, protein prices, incomes, gender, and initial height variables shown in Table \ref{summcovarmain} and described in Section \ref{sec:stat} as $N$, $H^{24}$, $p_{yv}^{N}$, $Y$, and components of $X$. We use protein intakes because \textcite{puentes_early_2016} shows that proteins rather than non-protein components of calories matter for height growth in these INCAP data. Ideally, our intake variable should be averaged from month 0 to month 24.\footnote{However, we do not observe protein values from month 0 to month 12 for close to half of our sample because data collection for this age group started in 1973. Also, it is not easy to estimate the protein component of breastmilk for children who rely on breastfeeding in the first year of life.}

@@

For $\rho$, the quadratic coefficient on non-nutritional consumptions, the estimated coefficient becomes more negative as $\sigma_{R_{y,v}}$ increases.\footnote{This finding implies lower marginal gains from additional non-nutritional consumption at higher $\sigma_{R_{y,v}}$.}

### 2022-05-15 template/fantemplate_acceptedsubmit/manuscript_title_etc.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{You are What Your Parents Expect: Height and Local Reference Points}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORWANG}{Fan Wang}
\newcommand{\AUTHORWANGINFO}{\AUTHORWANG: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 2. Define Title
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERTITLE}{\href{https://doi.org/10.1016/j.red.2021.09.001}{An equilibrium model of formal and informal credit markets in developing countries}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 3. Define Authors contact information
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\AUTHORWANG}{Fan Wang}
\newcommand{\AUTHORWANGURL}{https://orcid.org/0000-0003-2640-5420}
\newcommand{\AUTHORWANGINFO}{\href{\AUTHORWANGURL}{\AUTHORWANG}: Department of Economics, University of Houston, Houston, Texas, USA (email: fwang26@uh.edu)}

\newcommand{\AUTHORTEXFORECON}{Tex4Econ}
\newcommand{\AUTHORTEXFORECONURL}{https://fanwangecon.github.io/Tex4Econ/}
\newcommand{\AUTHORTEXFORECONINFO}{\href{\AUTHORTEXFORECONURL}{\AUTHORTEXFORECON}: Github repository, San Francisco, CA, USA (email: fanwecon@gmail.com)}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 6. Define citation or availability of latest draft
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERDOIURL}{https://doi.org/10.1086/711654}
\newcommand{\PAPERINFO}{
This paper has been accepted for publication: Hannum, Emily, Xiaoying Liu, and Fan Wang. “Estimating the Effects of Educational System Consolidation: The Case of China’s Rural School Closure Initiative.” Economic Development and Cultural Change 70, no. 1 (October 1, 2021): 485–528. \url{\PAPERDOIURL}.
}
